Master thesis

### 2017-06-01 index.Rmd
disqus test

--- 
site: "bookdown::bookdown_site"
title: "Master thesis"
author: "Sylvain SCHMITT"
date: "`r Sys.Date()`"
output: bookdown::gitbook
csl: bibliography/mee.csl
bibliography: bibliography/library.bib
link-citations: yes
colorlinks: yes
cover-image: images/main.png
---

>>>>

--- 
title: "Master thesis"
author: "Sylvain SCHMITT"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: 
  bookdown::gitbook
csl: /home/sylvain/Documents/Bibliography/csl/mee.csl
bibliography: /home/sylvain/Documents/Bibliography/library.bib
link-citations: yes
colorlinks: yes
cover-image: images/main.png
---
